High-resolution ALMA observations of V4046\,Sgr: a circumbinary disc with a thin ring

### 2020-12-07 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

Even though the radial spread of large dust grains in Ring13 appears to be quite thin, the width in comparison to the sub-lying gas profile speaks for the presence of non-negligible turbulent diffusion. Following a similar ring analysis as in \citet{2018ApJ...869L..46D}, we find that the ratio between the dimensionless diffusion parameter, $\alpha_{\rm diff}$, and the dimensionless Stokes number, St, (which parameterizes the dynamical behaviour of a grain) is roughly, $\alpha_{\rm diff}/{\rm St}\approx 0.1$. The observed signal is expected to be dominated by grains of size $a\approx 0.02\,{\rm cm}$, the RT model prescribes a gas density of $\Sigma_{\rm g} \approx 0.5\,{\rm g}{\rm cm}^{-2}$ to the location of Ring13. With these values, the relevant Stokes number is estimated to be St$\approx 0.1$. This yields an estimated level of diffusivity, $\alpha_{\rm diff}\approx 0.01$, and further provides a value for the level of turbulence, $\alpha$, in Ring13, as it is typically assumed to be equal to the level of diffusion \citep{2007Icar..192..588Y}. We note, that the obtained value of $\alpha \approx 0.01$ is larger than typical expectations \citep[e.g.][]{Flaherty_2020} and relies on not very well-constrained estimates of the gas density, as well as the fact that the width of Ring13 is measured at different vertical positions for small and large grains.

>>>>

Even though the radial spread of large dust grains in Ring13 appears to be quite thin, the width in comparison to the sub-lying gas profile speaks for the presence of considerable turbulent diffusion. Following a similar ring analysis as in \citet{2018ApJ...869L..46D}, we find that the ratio between the dimensionless diffusion parameter, $D$, and the dimensionless Stokes number, St, (which parameterizes the dynamical behaviour of a grain) is roughly, $D/{\rm St}\approx 0.1$. The observed signal is expected to be dominated by grains of size $a\approx 0.02\,{\rm cm}$, the RT model prescribes a gas density of $\Sigma_{\rm g} \approx 0.5\,{\rm g}{\rm cm}^{-2}$ to the location of Ring13. With these values, the relevant Stokes number is approximated to be St$\approx 0.1$. This yields an estimate for the level of diffusivity of $D\approx 0.01$. It further provides a value for the level of turbulence in Ring13, $\alpha_{\rm turb}\approx 0.01$, assuming turbulence to be equal to the level of diffusion \citep{2007Icar..192..588Y}. We note, that the obtained value for $\alpha_{\rm turb}$ is larger than typical expectations \citep[e.g.][for V4046 Sgr]{Flaherty_2020} and carries uncertainties originating from estimates of the local gas density, as well as the fact that the width of Ring13 is measured at different vertical positions for small and large grains in the observations.
